Price of Anarchy for Mean Field Games

### 2018-07-21 PoA.tex
update prop 6

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

%proposition b_2 \to 0
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
\end{proposition}

\begin{proof}
	    First, we consider $b_2 \to 0$. If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.
	As $b_2 \to 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm \delta^{\bar{b}_2 \to \infty},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty,$$
	$$\lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{} \delta^{\bar{b}_2 \to \infty} (r + \bar{r}(1-\bar{s})^2)=: c_3,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.

@@

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$. Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$. Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$. Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and 
	\begin{equation*}
	\begin{array}{rl}
	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot e^{- \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	Namely, for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

@@

 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for large enough $\bar{b}_2$.

@@

	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $0 \leq w^{\bar{b}_2 \to \infty}_0 < \infty$. Thus,
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV,\bar{b}_2} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA^{\bar{b}_2} = 1.$$
\end{proof}

>>>>

% proposition b_2 to \infty
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, then
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
\label{prop:b2_to_infty}
\end{proposition}

@@

%proposition b_2 \to 0
\begin{proposition}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

\begin{proof}
	If $\bar{b}_2 =0$, we can use the same technique in Proposition \ref{prop:r_bar_r} to show that $\lim_{b_2 \to 0} PoA = 1$. Now assume $\bar{b}_2 > 0$.

	As $b_2 \to 0$, we have $\lambda \to 0 $ and
	$$ B \to \frac{\bar{b}_2^2}{r + \bar{r}(1-\bar{s})^2}=:B^{0,b_2} >0,\ B^{\eta} \to 0,\ C^u \to 0,\ D^u \to 0.$$
	We also have $\delta^\pm_u \to -A^u \pm \vert A^u \vert $ and therefore, $\delta^{+}_u - \delta^{-}_u \to 2 \vert A^u \vert $. Thus, from equation (\ref{eq:riccati_ut_sol}) we deduce that for every fixed time $t \in [0,T]$:
	$$u_t \xrightarrow[b_2 \to 0 ]{} 0.$$

@@

	Now, for the case when $\bar{b}_2 \to \infty$,  we have $\lambda^{\bar{b}_2} \to 0$
	and $B^{\bar{b}_2} \to \infty,\ C^{u,\bar{b}_2} \to 0,\ D^{u,\bar{b}_2} \to 0$. It can be shown that:
	$$\lim_{\bar{b}_2 \to \infty}C^{u,\bar{b}_2}\sqrt{b_2+\bar{b}_2}=0,$$
	and
	$$ \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}} =\pm \sqrt{ \frac{b_2 (q + \bar{q}(1-s))}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta^{\bar{b}_2 \to \infty}_u},$$
	and therefore,
	$$\lim_{\bar{b}_2 \to \infty} \delta^{\pm,\bar{b}_2}_u=\pm \infty \qquad \text{and } \qquad \lim_{\bar{b}_2 \to \infty} \frac{\delta^{\pm,\bar{b}_2}_u}{b_2 + \bar{b}_2}=0.$$
	Also, note from the assumptions $q_T+\bar{q}_T(1-s_T)>0$ and $q_T+\bar{q}_T(1-s_T)^2>0$, we have $D^u>0$ and $D^w>0$. From equation (\ref{eq:riccati_ut_sol}), for $t \in [0,T)$ we can deduce:
	\begin{equation*}
	\begin{split}
	 	(b_2 + \bar{b}_2)^{\frac{3}{2}}\cdot u^{\bar{b}_2}_t =& \frac{ \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{+,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) - \left( C^{u,\bar{b}_2}\sqrt{b_2 + \bar{b}_2} + \zeta \cdot \frac{\delta^{-,\bar{b}_2}_u}{\sqrt{b_2 + \bar{b}_2}}  \right) e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_u}{b_2 + \bar{b}_2} + \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right) + \left( \frac{\delta^{+,\bar{b}_2}_u}{b_2 + \bar{b}_2} - \frac{b_2 (q_T + \bar{q}_T (1-s_T) )}{r + \bar{r}(1-\bar{s})} \right)e^{- (\delta^{+,\bar{b}_2}_u - \delta^{-,\bar{b}_2}_u)(T-t)} }\\
	 	& \xrightarrow[\bar{b}_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) c_{\delta^{\bar{b}_2 \to \infty}_u}=: c_3,
	 \end{split} 
	\end{equation*}
	where $\zeta = \frac{b_2 (r + \bar{r}(1-\bar{s})^2) }{r+ \bar{r}(1-\bar{s})} (q_T + \bar{q}_T(1-s_T))$.

@@

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We previously showed that $\lim_{\bar{b}_2 \to \infty}h(\bar{b}_2)= c_3 >0$. Let $\epsilon_1>0$ such that $c_3 - 2 \epsilon_1 >0$. Then there exists $\bar{b}_2^{*,1}>0$ so that for all $\bar{b}_2 > \bar{b}_2^{*,1}$ we have $\left\vert h(\bar{b}_2) - c_3 \right\vert < \epsilon_1$. Then $h(\bar{b}_2) - c_3 + 2\epsilon_1 > \epsilon_1$ and 
	\begin{equation*}
	\begin{array}{rl}
	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{1/2} h(\bar{b}_2) }  & 	\displaystyle  = e^{- \kappa (b_2 + \bar{b}_2)^{1/2} (h(\bar{b}_2) - c_3 + 2\epsilon_1 )}\cdot e^{- \kappa  (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} +  \ln (b_2 + \bar{b}_2) } \\
		&	\displaystyle  \leq  e^{- \kappa (b_2+\bar{b}_2^{*,1})^{1/2} \epsilon_1 } \cdot \exp \left( - \kappa (c_3 - 2 \epsilon_1 ) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)\right) \\
		%& 	\displaystyle  = c_5 e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2)^{1/2} + \ln (b_2 + \bar{b}_2)} \\
		%& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
	The first term on the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$. Thus,  for any $\epsilon>0$, there exists a $\bar{b}_2^{*,2} \geq \bar{b}_2^{*,1}$, such that for all $\bar{b}_2>\bar{b}_2^{*,2}$ we have:
	\begin{equation}
	|(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} h(\bar{b}_2) }|<\epsilon.
	\label{eq:limit_p_f(p)}
	\end{equation}

@@

 	\begin{comment}	
 	Idem, we can show that for $t_1 \in [0,T)$:
	\begin{equation*}
	\begin{split}
	(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} =&\frac{ \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{+,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) - \left( \frac{C^{w}}{b_2 + \bar{b}_2} + D^{w}\cdot \frac{\delta^{-,\bar{b}_2}_w}{b_2 + \bar{b}_2}  \right) e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T- t_1)}}{ \left(- \frac{\delta^{-,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} + \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right) + \left( \frac{\delta^{+,\bar{b}_2}_w}{(b_2 + \bar{b}_2)^2} - \frac{D^{w}}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,\bar{b}_2}_w - \delta^{-,\bar{b}_2}_w)(T-t_1)} }\\
	&\xrightarrow[\bar{b}_2 \to \infty]{} \sqrt{(r + \bar{r}(1-\bar{s})^2) C^w} =: c_4 >0,
	\end{split}
	\end{equation*}
	where we have used the fact that $\lim_{\bar{b}_2 \to \infty}\frac{\delta^{\pm,\bar{b}_2}_w}{b_2 + \bar{b}_2}=\sqrt{\frac{C^w}{r+\bar{r}(1-\bar{s})^2}}$. 
	\end{comment}
	Idem we can show that for any $t_1 \in [0,T)$:
	\begin{equation*}
		(b_2 + \bar{b}_2) w^{\bar{b}_2}_{t_1} \xrightarrow[\bar{b}_2 \to \infty]{} (r+ \bar{r}(1-\bar{s})^2) c_{\delta_w^{\bar{b}_2 \to \infty}} =: c_4, \qquad \text{where } \quad c_{\delta_w^{\bar{b}_2 \to \infty}} = \sqrt{\frac{q+ \bar{q}(1-s)^2}{r + \bar{r}(1 - \bar{s})^2} }.
	\end{equation*}
	Thus, $\left\vert w_{t_1}^{\bar{b}_2} \right\vert $ can also be bounded by $c_4 + \epsilon$ for any $\bar{b}_2$ large enough.

@@

	Moreover, recall that $\eta_t$ and $v_t$ are invariant with respect to $\bar{b}_2$ and $0<v_t<\infty$ for $t>0$. Clearly we also have $w^{\bar{b}_2}_0 \geq 0$ and $w^{\bar{b}_2}_0 \xrightarrow[\bar{b}_2 \to \infty]{} 0$. Thus, together with equation (\ref{eq:v_t_new_notation}) we obtain
	$$0< \lim_{\bar{b}_2 \to \infty} SC^{MKV} <\infty.$$
	Therefore, we conclude that:
	$$ \lim_{\bar{b}_2 \to \infty} PoA = 1.$$
\end{proof}
